Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-04-27 cav2017/cav2017.tex
+TODOs

@@

@@

Using the state-space models given in Section~\ref{experimental-setup}, 
our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}

@@

@@

\newpage
\appendix
%-------------------------------
\section{Stability of closed-loop models}
\label{sec:appendix-stability}
%-------------------------------

>>>>

\todo{Clarify challenges: FWL (rounding, truncation), quantisation (ADC, DAC).}

\todo{Discuss numerical (HSCC'17) vs. algorithmical soundness (CAV'17).}

@@

\todo{Refer to the SAS paper in this section.}

@@

Using the state-space models given in Section~\ref{experimental-setup}, 
our experimental evaluation aims to answer two research questions:
%

\todo{Remove RQ2 and only discuss the sanity check in 5.3?}

\begin{enumerate}

@@

\todo{Add the percentage of the total time taken by verification and synthesis.}

\todo{Discuss the number of abstraction refinements (inner loop, not the outer one)
  for the 2nd approach?
  Although, if it's always one, I'm not sure how interesting it is.. }

@@

\newpage
\appendix

\todo{Integrate Appendix in the actual paper.}

%-------------------------------
\section{Stability of closed-loop models}
\label{sec:appendix-stability}
%-------------------------------
